Longer term All-Cause and Cardiovascular Mortality with Intensive Blood Pressure Control: A Secondary Analysis of SPRINT

### 2024-07-05 doc/manuscript-rmd.Rmd
updated ndi

---
title: "Longer term All-Cause and Cardiovascular Mortality with Intensive Blood Pressure Control: A Secondary Analysis of SPRINT"
bibliography: refs.bib
csl: jama.csl
always_allow_html: true
output: 
  officedown::rdocx_document:
    reference_docx: style_manuscript_times_new_roman.docx
---
```{r setup, include=FALSE}

@@

@@

@@

@@

@@

# fpath <- file.path(
#   paste0(get_sasinet_drive(), ":"),
#   'bjaeger',
#   'sprint-mortality-ndi',
#   'fig',
#   'SPRINT_EHR_SBP_LongTerm_Comparison_122721.png'
# )
# 
# knitr::include_graphics(
#   path = fpath, 
#   dpi = 600
# )

@@

fpath <- file.path(
  get_sasinet_drive(),
  'bjaeger',
  'sprint-mortality-ndi',
  'fig',
  'sprint-ndi-timeline.png'
)

knitr::include_graphics(
  path = fpath,
  dpi = 600
)

@@

>>>>

---
title: "Longer term All-Cause and Cardiovascular Mortality with Intensive Blood Pressure Control: A Secondary Analysis of SPRINT"
bibliography: refs.bib
csl: jama.csl
always_allow_html: true
output: 
  officedown::rdocx_document:
    reference_docx: style_manuscript_times_new_roman.docx
    keep_md: true
---
```{r setup, include=FALSE}

@@

ggsave(filename = 'fig/figure1.pdf', 
       device = 'pdf', 
       dpi = knitr::opts_chunk$get("dpi"),
       width = knitr::opts_chunk$get("fig.width"), 
       height = knitr::opts_chunk$get("fig.height"))

@@

ggsave(filename = 'fig/figure2.pdf', 
       device = 'pdf', 
       dpi = knitr::opts_chunk$get("dpi"),
       width = knitr::opts_chunk$get("fig.width"), 
       height = knitr::opts_chunk$get("fig.height"))

@@

ggsave(filename = 'fig/figure3.pdf', 
       device = 'pdf', 
       dpi = knitr::opts_chunk$get("dpi"),
       width = knitr::opts_chunk$get("fig.width"), 
       height = knitr::opts_chunk$get("fig.height"))

@@

ggsave(filename = 'fig/figure4.pdf', 
       device = 'pdf', 
       dpi = knitr::opts_chunk$get("dpi"),
       width = knitr::opts_chunk$get("fig.width"), 
       height = knitr::opts_chunk$get("fig.height"))

@@

ggsave(filename = 'fig/figure5.pdf', 
       device = 'pdf', 
       dpi = knitr::opts_chunk$get("dpi"),
       width = knitr::opts_chunk$get("fig.width"), 
       height = knitr::opts_chunk$get("fig.height"))

@@

# fpath <- file.path(
#   # get_sasinet_drive(),
#   # 'bjaeger',
#   # 'sprint-mortality-ndi',
#   # 'fig',
#   'doc',
#   'sprint-ndi-timeline.png'
# )
# 
# knitr::include_graphics(
#   path = fpath,
#   dpi = 600
# )

@@

ggsave(filename = 'fig/figure6.pdf', 
       device = 'pdf', 
       dpi = knitr::opts_chunk$get("dpi"),
       width = knitr::opts_chunk$get("fig.width"), 
       height = knitr::opts_chunk$get("fig.height"))
